# **US Census Dataset**

### LA - 2 Exploratory Data Analysis

### Submitted By:- Shivee Jaiswal,1NT21IS152, 5 C

## ***Introduction***

#### The U.S. Census Dataset is a comprehensive collection of demographic, economic, and social data gathered by the United States Census Bureau. Conducted decennially, the census provides a detailed snapshot of the American population and serves as a crucial resource for policymakers, researchers, and businesses. The dataset covers a wide range of variables, including population counts, age distribution, racial and ethnic demographics, housing characteristics, income levels, educational attainment, and employment statistics. The census data plays a vital role in shaping public policies, resource allocation, and political representation. Additionally, it facilitates in-depth analyses of societal trends, disparities, and the overall well-being of the U.S. population. As a foundational tool for understanding the dynamics of American society, the U.S. Census Dataset contributes significantly to informed decision-making and informed social and economic research.

### Loading Libraries

```{r}
set.seed(123)

# Data manipulation

library(data.table)

library(dplyr)

library(DT)

# Time manipulation

library(lubridate)

# Visualization

library(ggplot2)

library(plotrix)

library(corrplot)

library(ggdendro)

library(ggrepel)

# Wordcloud

library(wordcloud)

# Text manipulation

library(tidytext)

library(stringr)

library(tm)

library(sentimentr)

library(wordcloud)

library(RSentiment)
```

```{r}
# Load the Dataset
df <- read.csv("C:\\Users\\Shivee Jaiswal\\Desktop\\acs2015_census_tract_data.csv")
# Data Summary
summary(df)

```

##Histogram Graph

```{r}
library(ggplot2)
ggplot(df, aes(x=Men)) +
  geom_histogram(colour="red")
```

# Frequency graph

```{r}
ggplot(df, aes(x=Men, y=Women)) +
  geom_col()
```

# Line Graph

```{r}
ggplot(df, aes(x=Men, y=TotalPop)) +
  geom_line(colour="blue")
```

# Point graph

```{r}
ggplot(df, aes(x=Women, y=TotalPop)) +
  geom_point()
```

# Boxplot

```{r}
ggplot(df, aes(x=White, y=Black)) +
  geom_boxplot(colour="yellow")
```

# Line graph

```{r}
ggplot(df, aes(x=Native)) +
  geom_line(stat="density", colour="brown") +
  expand_limits(y=0)
```

# Density graph

```{r}
ggplot(df, aes(x=Citizen, y=after_stat(density))) +
  geom_histogram(fill="cornsilk", colour="grey60", linewidth=.2) +
  geom_density() +
  xlim(500, 1050)

```

# Frequency polygon graph

```{r}
ggplot(df, aes(x=Income)) +
  geom_freqpoly() 
```

# Violin graph

```{r}
library(gcookbook)
df_p <- ggplot(df, aes(x= Men, y=Women)) 
df_p + geom_violin(adjust=2, colour="pink3")
```

# Correlation graph

```{r}
library(corrplot)
dfcorr <- data.frame(df$Men, df$Women, df$TotalPop)
dfcorr <- cor(dfcorr)
corrplot(dfcorr, method="square", shade.col= NA, tl.col="black", tl.srt=45)
```

```{r}
p <- ggplot(data.frame(x=c(-3,3)), aes(x=x))
p + stat_function(fun=dnorm)
```

# Network graph 

```{r}
library(igraph)
gd <- graph(c(1,2,2,3,2,4,1,4,5,5,3,6))
plot(gd)
```

```{r}
p <- ggplot(df, aes(x=Poverty, y=ChildPoverty))
p + geom_tile()
```

# Density graph

```{r}
library(ggplot2)

ggplot(df, aes(x = Men, fill = Women)) +
  geom_density(alpha = 0.5)
```

# Boxplot graph

```{r}
ggplot(head(df,50), aes(x = factor(White), y = Black, group = factor(White),fill=factor(White))) +
  geom_boxplot(width = 0.3) +  # Adjust the width as needed
  stat_summary(fun = "mean", geom = "point", shape = 18, size = 3, color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust x-axis label rotation if needed
```

# 2D Density graph

```{r}
ggplot(df, aes(x = Women, y = Men)) +
  geom_density_2d() +
  labs(x = "Women", y = "Men") +
  theme_minimal()
```

# Network graph

```{r}
library(igraph)

set.seed(42)  # for reproducibility

# Create a graph
graph <- graph.data.frame(df[, c("Men", "Women", "TotalPop")], directed = FALSE)

# Plot the network graph
plot(graph, 
     layout = layout_with_fr(graph),  # Use Fruchterman-Reingold layout
     vertex.label = NA,  # Display category_id as node labels
     edge.label = E(graph)$Women)  # Display views as edge labels
```

# Network graph

```{r}
set.seed(42)  # for reproducibility

# Create a graph
graph <- graph.data.frame(head(df,50)[, c("Men", "Women", "TotalPop")], directed = FALSE)

# Plot the network graph
plot(graph, 
     layout = layout.circle(graph),  # Use Fruchterman-Reingold layout
     vertex.label = NA,  # Display category_id as node labels
     edge.label = E(graph)$Men)  # Display views as edge labels
```

# Dot plot

```{r}
# Making a Dot Plot of US Census Dataset

dotchart(df$Men, pch = 19, col = "brown", main = "Dot Plot")
```

# Frequency graph

```{r}
# Making a Frequency Polygon for the US Census Dataset
plot(df$Women, type = "l", lty = 1, col = "pink", main = "Frequency Polygon")
```

# Curve function

```{r}
# Plotting a Function Curve for the given dataset
curve(x^2, from = -10, to = 10, col = "blue", lwd = 2)
```

### Github Link - https://github.com/shiveejaiswal/EDA
