# **Hotel Reviews **
## LA - 1 Exploratory Data Analysis
## Submitted By:- Shivee Jaiswal,1NT21IS152, 5 C
## ***Introduction***
#### The Hotel Reviews dataset is a collection of customer reviews and feedback about various hotels, providing valuable insights into the hospitality industry. Typically sourced from online review platforms or booking websites, this dataset encompasses a diverse range of hotels worldwide. Each review entry includes details such as the hotel's name, location, user ratings, and textual feedback from guests. Analyzing this dataset can offer profound insights into customer preferences, satisfaction levels, and specific aspects of hotels that influence their experiences. Researchers and businesses can leverage sentiment analysis and natural language processing techniques to extract sentiments expressed in these reviews, enabling them to understand trends, identify areas for improvement, and enhance overall customer satisfaction in the hotel industry. The Hotel Reviews dataset is a valuable resource for researchers, data scientists, and industry professionals aiming to gain a deeper understanding of customer opinions and preferences in the realm of hospitality.

```{r}
# Load the Dataset
data <- read.csv("C:\\Users\\Shatakshi\\Desktop\\Datafiniti_Hotel_Reviews.csv")
# Data Summary
summary(data)
```

```{r}
# Gives the structure
str(data)
```

```{r}
#To find missing values
any(is.na(data))
```

```{r}
# Retrieves the names of all the columns present in the dataset
names(data)
```

```{r}
# Outputs the initial rows of the dataset
head(data)
```

```{r}
# Outputs the summary of the dataset like max, min, Quartiles etc..
summary(data$latitude)
```

```{r}
# Outputs the standard deviation of the dataset
sd(data$longitude)
```

```{r}
sum(is.na(data))
```

```{r}
 # for data manipulation
library(dplyr)
```

```{r}
# visualizing interesting and interactive graphs
library(ggplot2)
```

```{r}

#Calculate mean of a specific column
 mean(data$latitude)

```

```{r}
#checking data type of a column
class(data$latitude)
```

```{r}

#Visualizing the latitude

height<- sort(table(data$latitude), decreasing = TRUE)

barplot(height[1:10], las = 3, main = "latitude")
```

```{r}
# Plotting a Function Curve for the given dataset
curve(x^2, from = -10, to = 10, col = "blue", lwd = 2)
```

```{r}
# Creating a Scatter Plot for latitude and longitude
library(ggplot2)
ggplot(data, aes(x = latitude, y = longitude)) + geom_point()
```



```{r}
# Making a Dot Plot of Hotel Review

dotchart(data$latitude, pch = 19, col = "brown", main = "Dot Plot")
```

```{r}
# generates a bar plot 
ggplot(data,aes(x= postalCode, fill = "#FF5733")) + geom_bar ()
```

```{r}
#View(tweets)
data[3:4,]
```

```{r}
ggplot(data) + aes(longitude,fill= longitude) + geom_bar() +geom_text(stat='count', aes(label=..count..), vjust=1.6, color="black")  + labs(title= 'Plot of longitude') +  theme_minimal() + guides(fill =  F)
```

```{r}
ggplot(data) + aes(latitude,fill= latitude) + geom_bar() +geom_text(stat='count', aes(label=..count..), vjust=1.6, color="black")  + labs(title= 'Plot of Sentiments') +
  scale_fill_manual(values = c("#ff576a","#3db5ff", "#66CC99"))+  theme_minimal() + guides(fill= F)
```

```{r}
ggplot(data, aes(x = latitude , fill = longitude))+ geom_bar( colour = 'black')  + scale_fill_manual(values = c("#ff576a","#3db5ff", "#66CC99")) + labs(x = 'latitude', y = 'longitude', title ='hotel review ') + theme(axis.text.x = element_text(angle = 25, size=9)) +  theme_minimal() + guides(fill= F)
```

```{r}
library(wordcloud)
```

```{r}

library(gganimate)
```

# ***Analysis***
#### The Hotel Reviews dataset provides a diverse collection of customer feedback, encompassing various hotels worldwide. Analyzing this dataset reveals valuable insights into customer preferences, satisfaction levels, and key factors influencing hotel experiences. Researchers can leverage sentiment analysis to extract sentiments from textual reviews, enabling a deeper understanding of overall trends and areas for improvement in the hospitality industry. The dataset facilitates comprehensive exploration of customer opinions, contributing to enhanced service quality and customer satisfaction strategies for hotel management.
```{r}
# Adding Means to a Box Plot
boxplot(data$latitude, mean = TRUE, col = "red", main = "Box Plot with Means")
```

```{r}
# Creating a Histogram for the hotel review
ggplot(data, aes(x = latitude)) + geom_histogram(binwidth = 5, fill = "blue", color = "black")
```

```{r}
# Making a Frequency Polygon for the hotel review
plot(data$latitude, type = "l", lty = 1, col = "pink", main = "Frequency Polygon")
```

```{r}
#Calculates the standard deviation a dataset
sd(data$latitude)

```

```{r}
#converting data type
as.numeric(data$longitude)
```

### Github Link - https://github.com/shiveejaiswal/EDA
